---
title: "living_seawalls_site_scale_map"
author: "Kyle Hilliam"
date: "2026-09-30"
output: html_document
editor_options: 
  chunk_output_type: console
---

Code developed using R version 4.5.1

Remote code repository location: https://github.com/KHilliam96/living_seawalls_global_analysis 

# Aim
-  
# To Do
-   

# Important Notes
-   

# Labelling System

-   .df, .list, .dist etc at the end of an object signify what class it is
-   iterations of an object where no significant change has occured will be noted numerically i.e., .df/.df2/.df3
-   df with spatial information and sf or sp objects will contain the coordinate system in their name, e.g., buffer_WGS1984.sf once transformed. But will not in first instance (buffer.df)

# Versioning
- V8 contains adjust SD for groups with NA values and sensitivity

# Setup

```{r setup, include = FALSE}
# https://bookdown.org/yihui/rmarkdown/r-code.html
knitr::opts_chunk$set(echo = FALSE, message = FALSE,
  warnings = FALSE, error = FALSE)

```

```{r packages, include = FALSE}
# Clear the space
rm(list = ls()) # clear memory

# Load packages
# Install and load pacman
if (!requireNamespace("pacman", quietly = TRUE)) {
  message("pacman is being installed and has been loaded.")
  install.packages("pacman")
  library(pacman)
} else {
  message("pacman is installed and has been loaded.")
  library(pacman)
}

# Data Wrangling
pacman::p_load(tidyverse)
pacman::p_load(snakecase)

# Spatial
pacman::p_load(leaflet)
pacman::p_load(leaflet.extras)
pacman::p_load(htmlwidget)
pacman::p_load(sf)
pacman::p_load(htmltools)
pacman::p_load(htmlwidgets)


```

```{r Set up versioning and outputs, include = FALSE}
update_data <- TRUE

# options(scipen = 999)
write_outputs     <- TRUE
project_directory <- "C:/Users/KyleHilliam/OneDrive - Sydney Institute of Marine Science/living_seawalls_repo/individual_papers/publications/meta_analysis_Kyle"
version <- "_V8"

geographic_data <- "C:/Users/KyleHilliam/OneDrive - Sydney Institute of Marine Science/living_seawalls_repo/project_data/geographic_data"
```

```{r File Locations, include = FALSE}
setwd(project_directory)
getwd()

# Get the location of our input data (this folder was created manually when
# saving the data)

inputs <- file.path(project_directory, "1_raw_inputs")

# All other folders can be created in the code (note, will only do this once)

# Create a directory to store current work in progress and files created in R

wip_r_directory <- file.path(project_directory, "2_wip_r")

if (!"work_in_progress_R" %in% basename(list.dirs(project_directory))) { # Check folder has not already been created
  
  dir.create(wip_r_directory)
  
  print("creating directory to store wip files")
  
} else {
  
  print("found existing wip directory")
  
}

# Create a directory to store current work in progress and files created in GIS

wip_gis_directory <- file.path(project_directory, "3_wip_non_code")

if (!"work_in_progress_GIS" %in% basename(list.dirs(project_directory))) { # Check folder has not already been created
  
  dir.create(wip_gis_directory)
  
  print("creating directory to store GIS wip files")
  
} else {
  
  print("found existing non-code wip directory")
  
}

# Create a directory to store all finalised outputs

processed_output_directory <- file.path(project_directory, "4_clean_outputs")

if (!"processed_outputs" %in% basename(list.dirs(project_directory))) { # Check folder has not already been created
  
  dir.create(processed_output_directory)
  
  print("creating directory to store outputs")
  
} else {
  
  print("found existing outputs directory")
  
}

# Create a directory to store all finalised figures

figure_directory <- file.path(project_directory, "5_manuscript_figures")

if (!"5_manuscript_figures" %in% basename(list.dirs(project_directory))) { # Check folder has not already been created
  
  dir.create(figure_directory)
  
  print("creating directory to store figures")
  
} else {
  
  print("found existing figure directory")
  
  
}  

# Create a directory to store all supplementary figures

supporting_directory <- file.path(project_directory, "6_supporting_figures")

if (!"6_supporting_figures" %in% basename(list.dirs(project_directory))) { # Check folder has not already been created
  
  dir.create(supporting_directory)
  
  print("creating directory to store figures")
  
} else {
  
  print("found existing supporting directory")
  
  
}
  
```

# Import data

## Site Data

```{r Copy site data across to inputs}
if(update_data){
      site_data_file <- list.files(geographic_data, 
                                      pattern = "site_info_ls_v1", 
                                      full.names = TRUE,
                                      recursive = TRUE)
      
      site_data_file
      
      # Copy the files
      file.copy(from = site_data_file,
                to   = file.path(inputs, basename(site_data_file)),
                overwrite = TRUE)
      message("Site data copied to inputs directory")
}

```

```{r Import Site Metadata}
site_data.df <- read_csv(file.path(inputs, "site_info_ls_v1.csv"))
```


# Manipulate

```{r Create SF object}
site.sf <- site_data.df %>%
                    filter(location %in% c("Balmain", "Blues Point", "clontarf", "cockatoo_island", "Condor", "fairlight", "Fan Pier", "east_fremantle", "keppel", "milsons_point", "plymouth", "rushcutters_bay", "sawmillers", "townsville"),
                           !is.na(lat),
                           !installation_type == "pilings"
                           ) %>%
                    dplyr::select(location, country, estuary, units, types, controls, site, site_type, lat, lon) %>%
                     sf::st_as_sf(coords = c("lon", "lat"), crs = 4326, remove = FALSE)
```

```{r Add Labels}
site.sf2 <- site.sf %>%
                mutate(location = to_title_case(location),
                       site = case_when(
                         grepl("con1", site) ~ "Control Seawall 1", 
                         grepl("con2", site) ~ "Control Seawall 2", 
                         grepl("con3", site) ~ "Control Seawall 3", 
                         grepl("con", site) ~ "Control Seawall 1", 
                         grepl("rs1", site) ~ "Reference Site 1", 
                         grepl("rs2", site) ~ "Reference Site 2", 
                         grepl("full", site) ~ "Living Seawall 1", 
                         grepl("par", site) ~ "Living Seawall 2", 
                         grepl("mod1", site) ~ "Living Seawall 1", 
                         grepl("mod2", site) ~ "Living Seawall 2", 
                         grepl("mod3", site) ~ "Living Seawall 3", 
                         grepl("mod", site) ~ "Living Seawall 1"),
                       popup = case_when(
                         site_type == "modified"  ~ paste0(location, ": ", site, " (", units, " panels), ", estuary, ", ", country),
                         site_type == "control"   ~ paste0(location, ": ", site, ", ", estuary, ", ",  country),
                         site_type == "reference" ~ paste0(location, ": ", site, ", ", estuary, ", ",  country)),
                       label = paste0(location, ": ", site,", ",  country))
```


# Create Leaflet Plot

```{r Create Leaflet object}
# Create Palette for circle markers
treat_pal <- colorFactor(palette = c(modified = "orange",
                                      control = "steelblue",
                                      reference = "forestgreen"),
                          domain = site.sf2$site_type)

# Add custom legend
site_legend <- HTML('
  <div style="background:white; padding:8px; border-radius:5px; font-size:12px; line-height:1.4;">
    <b>Site Type</b><br>
    <div><span style="display:inline-block; width:14px; height:14px; border-radius:50%; background:steelblue; border:1.5px solid black; margin-right:6px;"></span>Living Seawall</div>
    <div><span style="display:inline-block; width:14px; height:14px; border-radius:50%; background:orange; border:1.5px solid black; margin-right:6px;"></span>Control Seawall</div>
      <div><span style="display:inline-block; width:14px; height:14px; border-radius:50%; background:forestgreen; border:1.5px solid black; margin-right:6px;"></span><span style="font-style:normal;">Reference</span></div>
    </div>
')


# Create leaflet object
site_leaflet.plot <- leaflet(options = leafletOptions(maxZoom = 14)) %>%
                        setView(lng = 15, lat = 5, zoom = 2) %>%
                        addProviderTiles(providers$Esri.WorldGrayCanvas,
                                         group = "Esri Gray") %>%
                        addControl(html = "<div id='map-title' style='font-weight: bold;'>Interactive Site Map</div>", 
                                   position = "topright") %>%
                        addCircleMarkers(data = site.sf2,
                                         color = "black",
                                         weight = 0.5,
                                         fillColor = ~ treat_pal(site_type),
                                         radius = 12,
                                         opacity = 1,
                                         fillOpacity = 0.7,
                                         label = ~ label,
                                         popup = ~ popup,
                                         clusterOptions = markerClusterOptions(maxClusterRadius = 1,        
                                         disableClusteringAtZoom = 10)) %>%
                        addControl(html = site_legend,
                                    position = "bottomright") %>% # Add custom legend
                        addControl(html = "<div id='map-title'>Author: Kyle Hilliam</div>", position = "bottomleft") %>%
                        addScaleBar(position = "bottomleft",
                                    options =  scaleBarOptions(metric = TRUE,
                                        imperial = FALSE)) %>%
                        addEasyButton(easyButton(icon = "fa-globe",
                                                  title = "Reset View",
                                                  onClick = JS("function(btn, map){ map.setView([5, 15], 2); }"))) %>%
                        addMiniMap(tiles = providers$Esri.WorldGrayCanvas,  # match the default main map base layer
                                    toggleDisplay = TRUE,
                                    minimized = TRUE,
                                    position = "topleft") # add inset map


site_leaflet.plot

```

```{r Save the leaflet map}
if(write_outputs){
  
  saveWidget(site_leaflet.plot, 
             file = file.path(figure_directory, "site_scale_leaflet_v2.html"),
             selfcontained = TRUE)
  
  message("Site Scale leaflet map saved to ", file.path(figure_directory, "site_scale_leaflet_v2.html"))
}

```